---
title: "data comp"
---

### Introduction

Analysing customer data.

### ~ About Data ~

- id
- enquete_flag
- customer_id 
- gender
- age 
- registration_date
- withdrawal_date
- prefectures

#### About age column
- 1 = 10 ~ 19
- 2 = 20 ~ 24
- 3 = 25 ~ 29
- 4 = 30 ~ 34
- 5 = 35 ~ 39
- 6 = 40 ~

#### About gender column
  
- 1 = male
- 2 = female


#### About prefrectures column

1. Hokkaido
2. Aomori
3. Iwate
4. Miyagi
5. Akita
6. Yamagata
7. Fukushima
8. Ibaraki
9. Tochigi
10. Gunma
11. Saitama
12. Chiba
13. Tokyo
14. Kanagawa
15. Niigata
16. Toyama
17. Ishikawa
18. Fukui
19. Yamanashi
20. Nagano
21. Gifu
22. Shizuoka
23. Aichi
24. Mie
25. Shiga
26. Kyoto
27. Osaka
28. Hyogo
29. Nara
30. Wakayama
31. Tottori
32. Shimane
33. Okayama
34. Hiroshima
35. Yamaguchi
36. Tokushima
37. Kagawa
38. Ehime
39. Kochi
40. Fukuoka
41. Saga
42. Nagasaki
43. Kumamoto
44. Oita
45. Miyazaki
46. Kagoshima
47. Okinawa

### ~ Start Analyzing ~

#### Importing member.csv
```{r}
library(ggplot2)
member <- read.csv("~/Developer/dataComp/DataComp/Kazushi/data/member.csv", header = TRUE)
```

#### Creating a Pie chart of gender ratio
```{r}
genderRatio <- table(member$gender == 1)
genderHeader <- c(
  paste("(female)", genderRatio[1]),
  paste("(male)", genderRatio[2])
)
names(genderRatio) <- genderHeader
pie(genderRatio, col = rainbow(2))
```


#### Creating a Pie chart and a bar plot of age ratio

```{r}
ages <- member$age
agesRatio <- c(
  table(ages == 1)[2],
  table(ages == 2)[2],
  table(ages == 3)[2],
  table(ages == 4)[2],
  table(ages == 5)[2],
  table(ages == 6)[2]
)

agesHeader <- c(
  paste("(10 ~ 19)"),
  paste("(20 ~ 24)"),
  paste("(25 ~ 30)"),
  paste("(30 ~ 34)"),
  paste("(35 ~ 40)"),
  paste("(40 ~ )")
)
names(agesRatio) <- agesHeader

par(mfrow=c(1, 2))
pie(agesRatio, col = rainbow(20))
plot(agesRatio, col = rainbow(20))
```

#### Creating Stacked Bar Blot about Age and Gender

```{r}
malesByAge <- c()
femalesByAge <- c()
for(i in 1:6) {
  byAge <- member[member$age == i,]
  
  count <- length(byAge[byAge$gender == 1,][,1])
  malesByAge <- rbind(malesByAge, count)
  
  count <- length(byAge[byAge$gender == 2,][,1])
  femalesByAge <- rbind(femalesByAge, count)
}

data <- c()
data <- rbind(data, malesByAge[,1])
data <- rbind(data, femalesByAge[,1])

colnames(data) = 1:6

par(mfrow=c(1, 1))

barplot(
  as.matrix(data),
  col=rainbow(10),
  main="Stacked Bar Plot",
  legend.text = c("Male", "Female")
)
```


#### Creating bar plot of prefectures

```{r}
data <- c()
pref <- member$prefectures
for(i in 1:47) {
  count <- sum(pref == i)
  data <- cbind(data, count)
}

colnames(data) = 1:47

barplot(
  data,
  main = "Prefecture Distribution",
  xlab = "Prefecture Code",
  ylab = "Number of people"
)

```


